Environmental and geographic variables are effective surrogates for genetic variation in conservation planning

### 2016-11-10 code/rmarkdown/article.Rmd
+ update figure numberings

We created environmental and geographic surrogate variables for each species (Figures S59--S561). To describe the geographic location of each planning unit, we projected the grid into an equi-distant coordinate system (Europe Equidistant Conic; $\texttt{ESRI:102031}$), calculated the centroid of each grid cell, and extracted their two-dimensional coordinates. To describe the environmental characteristics of each planning unit, we obtained 19 climatic layers ($30^{\prime\prime}$ resolution; [@r33]), projected them and the planning units into an equal-area coordinate system (Europe Lambert Conformal Conic; $\texttt{ESRI:102014}$), and computed planning unit averages for each climatic variable. To reduce dimensionality, for each species, we subject the climatic values associated with their planning units to a principal components analysis (PCA; Table S1). We used the first `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` principal components to characterise climatic variation found across the species' distributions inside the study area (capturing `r round(mean(spp.pca.DF[[2]]*100),2)` % $\pm$ `r round(sd(spp.pca.DF[[2]]*100),2)` SD of the total climatic variation; Figure S2). Thus we constructed a two-dimensional geographic space as a potential surrogate for neutral genetic variation, and a `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))`-dimensional environmental space as a potential surrogate for adaptive genetic variation for each species. In these spaces, each planning unit was associated with a single point. Planning units with more similar environmental conditions, or higher spatial proximity in the real world, were associated with points that were closer together in these spaces (respectively).

@@

To investigate the effectiveness of our supposed surrogates, we quantified the main spatial patterns of adaptive and neutral genetic variation (Figures S59, S562). To do this, we first needed to identify which of the sampled loci were adaptive. Following best practices, we used two outlier detection methods to achieve this (an individual- and a population-level method; [@r495]). The basic premise underpinning such methods is that neutral loci are expected to exhibit a certain level of variation, and loci that deviate from this expectation are likely to be under selection ([@r480]). The advantage of these methods--in contrast to environmental association analyses--is that they do not use environmental data, which would have introduced circularity into our analysis. Loci identified as outliers in both analyses were treated as adaptive and the remainder were treated as neutral. To minimise false-positives, we omitted loci from both methods where the global frequency of the minor allele was less than 10 % and treated them as neutral.

>>>>

We created environmental and geographic surrogate variables for each species (see Figures S59--S561 for workflow). To describe the geographic location of each planning unit, we projected the grid into an equi-distant coordinate system (Europe Equidistant Conic; $\texttt{ESRI:102031}$), calculated the centroid of each grid cell, and extracted their two-dimensional coordinates. To describe the environmental characteristics of each planning unit, we obtained 19 climatic layers ($30^{\prime\prime}$ resolution; [@r33]), projected them and the planning units into an equal-area coordinate system (Europe Lambert Conformal Conic; $\texttt{ESRI:102014}$), and computed planning unit averages for each climatic variable. To reduce dimensionality, for each species, we subject the climatic values associated with their planning units to a principal components analysis (PCA; Table S1). We used the first `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))` principal components to characterise climatic variation found across the species' distributions inside the study area (capturing `r round(mean(spp.pca.DF[[2]]*100),2)` % $\pm$ `r round(sd(spp.pca.DF[[2]]*100),2)` SD of the total climatic variation; Figure S2). Thus we constructed a two-dimensional geographic space as a potential surrogate for neutral genetic variation, and a `r as.character(as.english(surrogate.params.LST[[MODE]]$number.components))`-dimensional environmental space as a potential surrogate for adaptive genetic variation for each species. In these spaces, each planning unit was associated with a single point. Planning units with more similar environmental conditions, or higher spatial proximity in the real world, were associated with points that were closer together in these spaces (respectively).

@@

To investigate the effectiveness of our supposed surrogates, we quantified the main spatial patterns of adaptive and neutral genetic variation (see Figures S59 and S62 for workflow). To do this, we first needed to identify which of the sampled loci were adaptive. Following best practices, we used two outlier detection methods to achieve this (an individual- and a population-level method; [@r495]). The basic premise underpinning such methods is that neutral loci are expected to exhibit a certain level of variation, and loci that deviate from this expectation are likely to be under selection ([@r480]). The advantage of these methods--in contrast to environmental association analyses--is that they do not use environmental data, which would have introduced circularity into our analysis. Loci identified as outliers in both analyses were treated as adaptive and the remainder were treated as neutral. To minimise false-positives, we omitted loci from both methods where the global frequency of the minor allele was less than 10 % and treated them as neutral.

### 2016-11-10 code/rmarkdown/supporting_information.Rmd
+ update figure numberings

  node[shape = ellipse, style = filled, color = darkslategray, fillcolor = white]
  calc_geo_as [label = 'Processing\n(Figure SXXX)'] 
  calc_env_as [label = 'Processing\n(Figure SXXX)']
  calc_genetic_as [label = 'Processing\n(Figure SXXX)']

>>>>

  node[shape = ellipse, style = filled, color = darkslategray, fillcolor = white]
  calc_geo_as [label = 'Processing\n(Figure S60)'] 
  calc_env_as [label = 'Processing\n(Figure S61)']
  calc_genetic_as [label = 'Processing\n(Figure S62)']
